SDR enhancement by clouds

### 2024-03-05 GHI_enh_04_investigate.tex
Commit 2024-03-05 11:13
Commit 2024-03-05 12:14
Commit 2024-03-05 13:12

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-02}

@@

lmD: 1.566022 +/- 0.1083205

lmY: 1.566038 +/- 0.1083224

Arima: 1.5664 0.1467 10.6787 0

@@

lmD: 0.9508227 +/- 0.1552488

lmY: 0.9508465 +/- 0.1552515

Arima: 1.0223 0.2369 4.315 0

@@

lmD: 1.087008 +/- 0.1678713

lmY: 1.087035 +/- 0.1678742

Arima: 1.16 0.2511 4.6199 0

@@

lmD: 33.66074 +/- 5.692733

lmY: 33.6613 +/- 5.692832

Arima: 33.7219 8.8826 3.7964 1e-04

@@

lmD: 0.003266094 +/- 0.0002706818

lmY: 0.003266127 +/- 0.0002706866

Arima: 0.0033 4e-04 9.0498 0

@@

lmD: 0.001714795 +/- 0.0002777698

lmY: 0.001714851 +/- 0.0002777746

@@

lmD: 0.001677055 +/- 0.00031363

lmY: 0.001677118 +/- 0.0003136354

Arima: 0.0018 5e-04 3.6151 3e-04

@@

lmD: 0.9770213 +/- 0.1439346

lmY: 0.9770437 +/- 0.1439371

Arima: 1.041 0.2186 4.7612 0

@@

lmD: 0.8175146 +/- 0.1034317

lmY: 0.8175255 +/- 0.1034336

Arima: 0.8175 0.12 6.8104 0

@@

lmD: 0.2160878 +/- 0.03807227

lmY: 0.2160919 +/- 0.03807295

Arima: 0.2161 0.0414 5.2173 0

@@

lmD: 0.1909484 +/- 0.03787569

lmY: 0.190953 +/- 0.03787636

Arima: 0.191 0.0401 4.7635 0

@@

lmD: 1467.856 +/- 152.6556

lmY: 1467.879 +/- 152.6584

Arima: 1467.8755 184.369 7.9616 0

@@

lmD: 0.001335923 +/- 0.0001367163

lmY: 0.001335939 +/- 0.0001367188

Arima: 0.0013 2e-04 8.5092 0

@@

lmD: 0.000422753 +/- 5.903214e-05

lmY: 0.0004227591 +/- 5.903319e-05

Arima: 4e-04 1e-04 6.291 0

@@

lmD: 0.000372438 +/- 6.132797e-05

lmY: 0.0003724446 +/- 6.132906e-05

Arima: 4e-04 1e-04 5.4467 0

@@

lmD: 0.03656094 +/- 0.003621568

lmY: 0.03656157 +/- 0.003621632

@@

lmD: 0.1872432 +/- 0.2494753

lmY: 0.1872803 +/- 0.2494792

Arima: 0.1718 0.3646 0.4712 0.6375

@@

lmD: 0.0498083 +/- 0.192504

lmY: 0.04983275 +/- 0.1925071

Arima: 0.0086 0.3464 0.0248 0.9802

@@

lmD: 0.0912832 +/- 0.1914519

lmY: 0.09130632 +/- 0.191455

Arima: 0.05 0.3354 0.1491 0.8815

@@

lmD: 0.3683616 +/- 0.2534977

lmY: 0.3683881 +/- 0.2535018

@@

lmD: 0.0005085756 +/- 0.0002811408

lmY: 0.0005085833 +/- 0.0002811453

Arima: 5e-04 3e-04 1.598 0.11

@@

lmD: 0.0003565528 +/- 0.0002141263

lmY: 0.0003565519 +/- 0.0002141297

Arima: 3e-04 3e-04 1.3206 0.1866

@@

lmD: 0.000398809 +/- 0.0002210804

lmY: 0.0003988093 +/- 0.0002210839

Arima: 4e-04 3e-04 1.4507 0.1469

@@

lmD: 0.008776506 +/- 0.00550671

lmY: 0.008777009 +/- 0.005506798

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/groups-9} \end{center}

@@

@@

\begin{verbatim}
2024-03-02 12:29:58.0 athan@tyler GHI_enh_04_investigate.R 1.354976 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-03-05}

@@

lmD: 1.566006 +/- 0.1083205

lmY: 1.566022 +/- 0.1083224

Arima: 1.5664 0.1467 10.6786 0

@@

lmD: 0.9508037 +/- 0.1552487

lmY: 0.9508275 +/- 0.1552514

Arima: 1.0223 0.2369 4.3149 0

@@

lmD: 1.086985 +/- 0.1678711

lmY: 1.087013 +/- 0.1678741

Arima: 1.16 0.2511 4.6198 0

@@

lmD: 33.66024 +/- 5.69273

lmY: 33.6608 +/- 5.692829

Arima: 33.7214 8.8815 3.7968 1e-04

@@

lmD: 0.003266044 +/- 0.0002706817

lmY: 0.003266077 +/- 0.0002706865

Arima: 0.0033 4e-04 9.0497 0

@@

lmD: 0.001714761 +/- 0.0002777697

lmY: 0.001714817 +/- 0.0002777745

@@

lmD: 0.001677019 +/- 0.0003136298

lmY: 0.001677082 +/- 0.0003136353

Arima: 0.0018 5e-04 3.615 3e-04

@@

lmD: 0.9770065 +/- 0.1439346

lmY: 0.9770288 +/- 0.1439371

Arima: 1.041 0.2186 4.7611 0

@@

lmD: 0.8175029 +/- 0.1034317

lmY: 0.8175138 +/- 0.1034336

Arima: 0.8175 0.12 6.8102 0

@@

lmD: 0.216071 +/- 0.03807207

lmY: 0.2160751 +/- 0.03807275

Arima: 0.2161 0.0414 5.2169 0

@@

lmD: 0.190931 +/- 0.03787542

lmY: 0.1909357 +/- 0.03787609

Arima: 0.1909 0.0401 4.7631 0

@@

lmD: 1467.857 +/- 152.6559

lmY: 1467.88 +/- 152.6586

Arima: 1467.8769 184.2435 7.967 0

@@

lmD: 0.00133588 +/- 0.0001367161

lmY: 0.001335895 +/- 0.0001367186

Arima: 0.0013 2e-04 8.5089 0

@@

lmD: 0.0004227125 +/- 5.903165e-05

lmY: 0.0004227187 +/- 5.90327e-05

Arima: 4e-04 1e-04 6.2905 0

@@

lmD: 0.0003723972 +/- 6.132751e-05

lmY: 0.0003724038 +/- 6.13286e-05

Arima: 4e-04 1e-04 5.4462 0

@@

lmD: 0.03656091 +/- 0.003621574

lmY: 0.03656153 +/- 0.003621638

@@

lmD: 0.1872084 +/- 0.2494764

lmY: 0.1872455 +/- 0.2494804

Arima: 0.1718 0.3646 0.4711 0.6376

@@

lmD: 0.04977389 +/- 0.1925048

lmY: 0.04979834 +/- 0.1925079

Arima: 0.0085 0.3464 0.0247 0.9803

@@

lmD: 0.0912485 +/- 0.1914527

lmY: 0.09127162 +/- 0.1914558

Arima: 0.05 0.3354 0.149 0.8816

@@

lmD: 0.368357 +/- 0.2534977

lmY: 0.3683834 +/- 0.2535018

@@

lmD: 0.0005084984 +/- 0.0002811406

lmY: 0.0005085061 +/- 0.0002811451

Arima: 5e-04 3e-04 1.5978 0.1101

@@

lmD: 0.000356478 +/- 0.0002141255

lmY: 0.0003564771 +/- 0.0002141289

Arima: 3e-04 3e-04 1.3203 0.1867

@@

lmD: 0.0003987357 +/- 0.0002210796

lmY: 0.0003987361 +/- 0.0002210831

Arima: 4e-04 3e-04 1.4505 0.1469

@@

lmD: 0.008776338 +/- 0.005506711

lmY: 0.00877684 +/- 0.005506799

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/clim_CE_N_doy-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_daily-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/climCE_week-1} \end{center}

@@

\begin{verbatim}
2024-03-05 09:51:07.3 athan@tyler GHI_enh_04_investigate.R 1.319722 mins
\end{verbatim}

### 2024-03-05 article/article.Rmd
Commit 2024-03-05 13:12

>>>>

## New plots for discusion

### Climatology

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per week"}
knitr::include_graphics("../images/climCE_week-1.png")
```

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
knitr::include_graphics("../images/climCE_daily-1.png")
```

```{r echo=FALSE, fig.cap="Distribution of the number of CE cases per doy"}
knitr::include_graphics("../images/clim_CE_N_doy-1.png")
```
